Prefetching SPARQL query cacher

### 2016-06-05 dissertation/cache-proxy.tex
add todo on cost model based on doe
move the todo

\begin{table}
\caption{The modules that enable the query cache\todo{make it fit. Rotate?}}\label{tab:modules}
\begin{tabular}{ | l | p{3cm} | l |}
  \hline
  Module & Authors & Github URL \\ \hline

@@

  \hline
\end{tabular}
\end{table}

@@

If the experiment outlined here could come to fruition, and we take
the factor in the first point with level~1 as the cache being enabled,
then we can examine the experiment similarly to what with did with the
``Implement'' factor in \cite{kjernsmo_doe_intro}. That is, the first
step to understand the contributions to the endpoint system load by
the different factors, is to create a normal plot and then use the
Lenth criterion for significance. For the next step, to test the
alternative hypothesis that the endpoint system load has decreased,
form an average of the effects for all combinations of the factor in
point~1 and the insignificant factors determined in the first step,
based on the average over the rest of the factors. Based on this, a
common one-sided two-sample $t$-test can be performed.

>>>>

\begin{table}
\caption{The modules that enable the query cache}\label{tab:modules}
\begin{tabular}{ | l | p{3cm} | l |}
  \hline
  Module & Authors & Github URL \\ \hline

@@

  \hline
\end{tabular}
\end{table}
\todo{make it fit. Rotate?}

@@

If the experiment outlined here could come to fruition, and we take
the factor in the first point with level~1 as the cache being enabled,
then we can examine the experiment similarly to what with did with the
``Implement'' factor in \cite{kjernsmo_doe_intro}. That is, the first
step to understand the contributions to the endpoint system load by
the different factors, is to create a normal plot and then use the
Lenth criterion for significance. For the next step, to test the
alternative hypothesis that the endpoint system load has decreased,
form an average of the effects for all combinations of the factor in
point~1 and the insignificant factors determined in the first step,
based on the average over the rest of the factors. Based on this, a
common one-sided two-sample $t$-test can be performed.\todo{Discuss
  cost model based on DoE?}
